### 2025-09-21 submissions/03-jpam-RR/manuscript_main.tex
do margins

@@

@@

I report main results from estimating equation (\ref{eq:identity_reg_bias}) in Figure (\ref{plot01-regression-gen}). I present results estimating the main specification for all generations in panel (A) and for first-, second-, and third-generation subsamples in panels (B), (C), and (D), respectively. Anti-Asian bias and Asian racial identity reporting exhibit negative associations. One standard deviation anti-Asian bias increases correlate with 9 percentage point decreases in Asian racial identity reporting. Among first- and second-generation Asian Americans, one standard deviation anti-Asian bias increases associate with 5 and 8 percentage point decreases in Asian racial identity reporting. The first-generation coefficient lacks statistical significance, but confidence intervals remain predominantly negative. Among third-generation Asian Americans, one standard deviation anti-Asian bias increases associate with 8 percentage point decreases in Asian racial identity reporting. Moreover, I find that---among all objectively Asian individuals---having a college-educated father or mother increases Asian racial identity reporting by 1 percentage point.\footnote{I show the results using county-level and MSA-level anti-Asian bias measures from the Implicit Association Test (IAT) show similar patterns. I present the county-level results in Figures \ref{plot01-regression-gen-county} and \ref{plot01-regression-byparent-county}, while I show the MSA-level in Figures \ref{plot01-regression-gen-msa} and \ref{plot01-regression-byparent-msa}.} \footnote{I present linear probability model (LPM) results alongside logit and probit estimations with marginal effects to demonstrate the consistency of findings across different functional forms. Tables \ref{regtab-all-gen}-\ref{regtab-third-gen} show that the marginal effects from logit and probit models closely align with the LPM coefficients across all generations, providing confidence in the estimated relationships between anti-Asian bias and racial identity reporting regardless of modeling approach.}

I report the results using adult samples in Figure (\ref{plot01-regression-gen-adults}). I present results estimating the main specification for all adults in panel (A) and for first- and second-generation subsamples in panels (B) and (C), respectively. Anti-Asian bias and Asian racial identity reporting exhibit negative associations. One standard deviation anti-Asian bias increases correlate with 5 percentage point decreases in Asian racial identity reporting. Among first-generation Asian American adults, one standard deviation anti-Asian bias increases associate with 2 percentage point decreases in Asian racial identity reporting but is statistically insignificant. Among second-generation Asian American adults, one standard deviation anti-Asian bias increases associate with 13 percentage point decreases in Asian racial identity reporting.

I report identical regression results for second-generation immigrant subsamples by parent type—interracial versus endogamous parents—in Figure (\ref{plot01-regression-byparent}). I present main specification results for second-generation immigrants in panel (A) and for AA, AW, and WA children subsamples in panels (B), (C), and (D), respectively. Children from interracial families show greater bias influence. One standard deviation anti-Asian bias increases associate with 5 percentage point decreases in Asian racial identity reporting among endogamous parent children—estimates are statistically insignificant. However, one standard deviation anti-Asian bias increases associate with 15 percentage point decreases in Asian racial identity reporting among Asian father-White mother children, and 10 percentage point decreases among White father-Asian mother children.

I report the results using adult samples in Figure (\ref{plot01-regression-byparent-adults}). I present results estimating the main specification for all second-generation adults in panel (A) and for AA, AW, and WA children subsamples in panels (B), (C), and (D), respectively. One standard deviation anti-Asian bias increases associate with 13 percentage point decreases in Asian racial identity reporting among second-generation adults. Among second-generation adults with endogamous parents, one standard deviation anti-Asian bias increases associate with 10 percentage point decreases in Asian racial identity reporting but are statistically insignificant. However, one standard deviation anti-Asian bias increases associate with a statistically insignificant 3 percentage point decreases in Asian racial identity reporting among Asian father-White mother adults, and 24 percentage point decreases among White father-Asian mother adults.

I also report regression results for third-generation immigrant subsamples by Asian grandparent numbers in Table (\ref{regtab-bygrandparents}). Overall anti-Asian bias effects on different Asian American children types are negative but mostly statistically insignificant. One standard deviation anti-Asian bias increases associate with 69 percentage point decreases in Asian racial identity reporting among Asian American children with three Asian-born grandparents.

>>>>

Moreover, to further understand how explanatory variables affect Asian racial identity reporting, I estimate a multinomial logit model replacing the dependent variable $A_{ist}^g$ with categorical racial identity choices: (1) Asian only, (2) White only, (3) Asian and White/Pacific Islander. The equation is as follows:

\begin{align}
\log\left(\frac{P(Y_{ist}^g = j)}{P(Y_{ist}^g = \text{Asian only})}\right) &= \beta_{1j}^g AntiAsianBias_{st} + \beta_{2j}^g DadCollegeGrad_{ist}\nonumber \\ 
& + \beta_{3j}^g MomCollegeGrad_{ist} + \beta_{4j}^g Female_{ist} + X_{ist}^g\pi_j  \nonumber \\ 
& + \gamma_{rtj} + \varepsilon_{istj}; \quad j \in \{\text{White only}, \text{Asian and White}\} \label{eq:multinomial_logit}
\end{align}

where $Y_{ist}$ represents the categorical racial identity of person $i$ in state $s$ at interview time $t$, $j$ indexes the identity categories, with "Asian only" as the reference category, $P(Y_{ist}^g = j)$ denotes the probability of person $i$ in state $s$ at time $t$ choosing identity $j$, $\mathbf{X}_{ist}^g$ represents the vector of controls that include quartic age, Asian population fraction, parent types, grandparent types, and generation dummies, $\boldsymbol{\beta}_j^g$ denotes the coefficient vector for outcome $j$ and generation $g$, and $J$ indexes the three identity categories. Finally, $\gamma_{rtj}$ represents region-time fixed effects that would control for region $\times$ year specific shocks affecting identity choice $j$, and $\varepsilon_{istj}$ is the error term.

The model specification allows the effects of anti-Asian bias and other covariates to vary across identity choices. For instance, $\beta_{1,\text{White only}}^g$ captures how anti-Asian bias affects the log-odds of choosing "White only" versus "Asian only" identity, while $\beta_{1,\text{Asian and White}}^g$ measures the bias effect on choosing "Asian and White" versus "Asian only." This framework enables analysis of how bias, sex, and parental education differentially influences various identity strategies available to individuals with Asian ancestry.

The coefficients of interest are $\beta_{1j}^g$, $\beta_{2j}^g$, $\beta_{3j}^g$ and $\beta_{4j}^g$, which capture how anti-Asian bias, parental education, and sex influence the likelihood of selecting each identity category relative to "Asian only." I estimate separate models for each generation $g \in \{1,2,3\}$ to assess whether these relationships differ across generational status.

The multinomial specification proves particularly appropriate for analyzing Asian American identity choices because it accounts for the distinct utility individuals may derive from different identity options. Unlike binary choice models, the multinomial framework recognizes that choosing "White only" identity represents a fundamentally different strategy than selecting "Asian and White" multiracial identification, even though both alternatives to "Asian only" may respond to anti-Asian bias. This distinction is particularly important for mixed-ancestry individuals, who may strategically choose between complete ethnic distancing (reporting "White only") versus maintaining partial ethnic connection through multiracial identification ("Asian and White").

Since log odds coefficients from multinomial logit models are difficult to interpret directly, I estimate marginal effects to interpret coefficients, calculating how a one-unit change in each covariate affects the probability of selecting each identity category. For binary variables such as parental education, I calculate discrete changes in predicted probabilities when the variable shifts from zero to one, holding all other covariates at their sample means.

@@

\subsection*{Dichotomous Asian Racial Identity Reporting and Anti-Asian Bias}

@@

I report main results from estimating equation (\ref{eq:identity_reg_bias}) in Figure (\ref{plot01-regression-gen}). I present results estimating the main specification for all generations in panel (A) and for first-, second-, and third-generation subsamples in panels (B), (C), and (D), respectively. Anti-Asian bias and Asian racial identity reporting exhibit negative associations. One standard deviation anti-Asian bias increases correlate with 9 percentage point decreases in Asian racial identity reporting. Among first- and second-generation Asian Americans, one standard deviation anti-Asian bias increases associate with 5 and 8 percentage point decreases in Asian racial identity reporting. The first-generation coefficient lacks statistical significance, but confidence intervals remain predominantly negative. Among third-generation Asian Americans, one standard deviation anti-Asian bias increases associate with 8 percentage point decreases in Asian racial identity reporting. Moreover, I find that---among all objectively Asian individuals---having a college-educated father or mother increases Asian racial identity reporting by 1 percentage point.\footnote{I show the results using county-level and MSA-level anti-Asian bias measures from the Implicit Association Test (IAT) show similar patterns. I present the county-level results in Figures \ref{plot01-regression-gen-county} and \ref{plot01-regression-byparent-county}, while I show the MSA-level in Figures \ref{plot01-regression-gen-msa} and \ref{plot01-regression-byparent-msa}.} \footnote{I present linear probability model (LPM) results alongside logit and probit estimations with marginal effects to demonstrate the consistency of findings across different functional forms. Tables \ref{regtab-all-gen}-\ref{regtab-third-gen} show that the marginal effects from logit and probit models closely align with the LPM coefficients across all generations, providing confidence in the estimated relationships between anti-Asian bias and racial identity reporting regardless of modeling approach.} Examining the effect of parental education and sex, I observe that gender has minimal effects on Asian identity reporting across most specifications. Parental education effects vary by generation: among second-generation immigrants, both maternal and paternal college education show positive associations with Asian identity reporting, while among third-generation immigrants, the effects are smaller and sometimes statistically insignificant.

I report the results using adult samples in Figure (\ref{plot01-regression-gen-adults}). I present results estimating the main specification for all adults in panel (A) and for first- and second-generation subsamples in panels (B) and (C), respectively. Anti-Asian bias and Asian racial identity reporting exhibit negative associations. One standard deviation anti-Asian bias increases correlate with 5 percentage point decreases in Asian racial identity reporting. Among first-generation Asian American adults, one standard deviation anti-Asian bias increases associate with 2 percentage point decreases in Asian racial identity reporting but is statistically insignificant. Among second-generation Asian American adults, one standard deviation anti-Asian bias increases associate with 13 percentage point decreases in Asian racial identity reporting. The adult specifications reveal additional socioeconomic influences: higher household income and years of education both positively correlate with Asian identity reporting, with each additional year of education associated with approximately 1-2 percentage point increases in the probability of reporting Asian identity.

I report identical regression results for second-generation immigrant subsamples by parent type—interracial versus endogamous parents—in Figure (\ref{plot01-regression-byparent}). I present main specification results for second-generation immigrants in panel (A) and for AA, AW, and WA children subsamples in panels (B), (C), and (D), respectively. Children from interracial families show greater bias influence. One standard deviation anti-Asian bias increases associate with 5 percentage point decreases in Asian racial identity reporting among endogamous parent children—estimates are statistically insignificant. However, one standard deviation anti-Asian bias increases associate with 15 percentage point decreases in Asian racial identity reporting among Asian father-White mother children, and 10 percentage point decreases among White father-Asian mother children. Among endogamous Asian families, maternal college education consistently shows positive effects on children's Asian identity reporting. In contrast, among mixed-race families, the effects of parental education are more heterogeneous, with college-educated mothers in Asian father-White mother families showing particularly strong positive associations with Asian identity reporting.

I report the results using adult samples in Figure (\ref{plot01-regression-byparent-adults}). I present results estimating the main specification for all second-generation adults in panel (A) and for AA, AW, and WA children subsamples in panels (B), (C), and (D), respectively. One standard deviation anti-Asian bias increases associate with 13 percentage point decreases in Asian racial identity reporting among second-generation adults. Among second-generation adults with endogamous parents, one standard deviation anti-Asian bias increases associate with 10 percentage point decreases in Asian racial identity reporting but are statistically insignificant. However, one standard deviation anti-Asian bias increases associate with a statistically insignificant 3 percentage point decreases in Asian racial identity reporting among Asian father-White mother adults, and 24 percentage point decreases among White father-Asian mother adults. Among endogamous Asian families, maternal college education consistently shows positive effects on children's Asian identity reporting. In contrast, among mixed-race families, the effects of parental education are more variable, with college-educated mothers in Asian father-White mother families showing particularly strong positive associations with Asian identity reporting.

I also report regression results for third-generation immigrant subsamples by Asian grandparent numbers in Table (\ref{regtab-bygrandparents}). Overall anti-Asian bias effects on different Asian American children types are negative but mostly statistically insignificant. One standard deviation anti-Asian bias increases associate with 69 percentage point decreases in Asian racial identity reporting among Asian American children with three Asian-born grandparents. The demographic and family characteristics reveal interesting patterns by grandparent composition. Female gender is associated with lower Asian identity reporting among those with four Asian grandparents, while parental education effects are strongest among those with two Asian grandparents, where maternal college education increases Asian identity reporting by 7 percentage points.

\subsection*{Multinomial Logit Results: Racial Identity Choices and Anti-Asian Bias}

### 2025-09-21 submissions/03-jpam-RR/manuscript_tab_fig.tex
do margins

>>>>

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Predicted Probabilities: All Generations}
\label{fig:pp-all-gen}

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{simple_pp_value_all.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{simple_pp_Female_all.png}
\end{subfigure}

\vspace{0.5cm}

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{simple_pp_MomGradCollege_all.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{simple_pp_DadGradCollege_all.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from the multinomial logit model for all generations. The model estimates the probability of choosing "Asian only", "White only", or "Asian and White" racial identification as a function of covariates. All other variables are held at their sample means. The analysis includes first-, second-, and third-generation Asian Americans.}}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Predicted Probabilities: Second Generation Asian Father-White Mother (AW)}
\label{fig:pp-second-aw}

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{simple_pp_value_second_aw.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{simple_pp_Female_second_aw.png}
\end{subfigure}

\vspace{0.5cm}

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{simple_pp_MomGradCollege_second_aw.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{simple_pp_DadGradCollege_second_aw.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from the multinomial logit model for second-generation Asian Americans with Asian fathers and White mothers. The model estimates the probability of choosing "Asian only", "White only", or "Asian and White" racial identification as a function of covariates. All other variables are held at their sample means.}}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Predicted Probabilities: Second Generation White Father-Asian Mother (WA)}
\label{fig:pp-second-wa}

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{simple_pp_value_second_wa.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{simple_pp_Female_second_wa.png}
\end{subfigure}

\vspace{0.5cm}

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{simple_pp_MomGradCollege_second_wa.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{simple_pp_DadGradCollege_second_wa.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from the multinomial logit model for second-generation Asian Americans with White fathers and Asian mothers. The model estimates the probability of choosing "Asian only", "White only", or "Asian and White" racial identification as a function of covariates. All other variables are held at their sample means.}}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Predicted Probabilities: Third Generation One Asian Grandparent}
\label{fig:pp-third-one}

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{simple_pp_value_third_one.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{simple_pp_Female_third_one.png}
\end{subfigure}

\vspace{0.5cm}

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{simple_pp_MomGradCollege_third_one.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{simple_pp_DadGradCollege_third_one.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from the multinomial logit model for third-generation Asian Americans with one Asian grandparent. The model estimates the probability of choosing "Asian only", "White only", or "Asian and White" racial identification as a function of covariates. All other variables are held at their sample means.}}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Predicted Probabilities: Third Generation Two Asian Grandparents}
\label{fig:pp-third-two}

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{simple_pp_value_third_two.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{simple_pp_Female_third_two.png}
\end{subfigure}

\vspace{0.5cm}

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{simple_pp_MomGradCollege_third_two.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{simple_pp_DadGradCollege_third_two.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from the multinomial logit model for third-generation Asian Americans with two Asian grandparents. The model estimates the probability of choosing "Asian only", "White only", or "Asian and White" racial identification as a function of covariates. All other variables are held at their sample means.}}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[!htb]
\centering
\caption{Predicted Probabilities: Third Generation Three Asian Grandparents}
\label{fig:pp-third-three}

\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias}
\centering
\includegraphics[width=1\linewidth]{simple_pp_value_third_three.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female}
\centering
\includegraphics[width=1\linewidth]{simple_pp_Female_third_three.png}
\end{subfigure}

\vspace{0.5cm}

\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Mother}
\centering
\includegraphics[width=1\linewidth]{simple_pp_MomGradCollege_third_three.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{College Graduate: Father}
\centering
\includegraphics[width=1\linewidth]{simple_pp_DadGradCollege_third_three.png}
\end{subfigure}

\caption*{\footnotesize{This figure shows predicted probabilities from the multinomial logit model for third-generation Asian Americans with three Asian grandparents. The model estimates the probability of choosing "Asian only", "White only", or "Asian and White" racial identification as a function of covariates. All other variables are held at their sample means.}}
\end{figure}
\end{center}

### 2025-09-21 submissions/03-jpam-RR/submit_journal.tex
do margins

            % To further explore how explanatory variables influence these identity choices, I have re-estimated my main models using multinomial logistic regression. This approach allows me to model the probabilities of reporting ``Asian only,'' ``White only,'' and ``Asian and White/Pacific Islander'' as separate outcomes. The results, presented in Tables \ref{regtab-mnl-all-gen}-\ref{regtab-mnl-third-gen}, reveal that anti-Asian bias significantly decreases the likelihood of reporting ``Asian only'' while increasing the probabilities of both ``White only'' and ``Asian and White/Pacific Islander'' identifications among mixed-ancestry individuals. For example, among second-generation children from Asian father-White mother families, a one standard deviation increase in anti-Asian bias is associated with a 12 percentage point decrease in the probability of reporting ``Asian only,'' a 7 percentage point increase in ``White only,'' and a 5 percentage point increase in ``Asian and White/Pacific Islander.''

>>>>

            To further explore how explanatory variables influence these identity choices, I added results from estimating the effects of bias, parental education, and sex using a multinomial logistic regression. This approach allows me to model the probabilities of reporting ``Asian only,'' ``White only,'' and ``Asian and White/Pacific Islander'' as separate outcomes.

            % The results, presented in Figures \ref{}-\ref{regtab-mnl-third-gen}, reveal that anti-Asian bias significantly decreases the likelihood of reporting ``Asian only'' while increasing the probabilities of both ``White only'' and ``Asian and White/Pacific Islander'' identifications among mixed-ancestry individuals. For example, among second-generation children from Asian father-White mother families, a one standard deviation increase in anti-Asian bias is associated with a 12 percentage point decrease in the probability of reporting ``Asian only,'' a 7 percentage point increase in ``White only,'' and a 5 percentage point increase in ``Asian and White/Pacific Islander.''
